% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{David C. Jinkins}

% Replace this with a link to your CV if you like, or set it empty
 %(as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{http://www.davidjinkins.com/CV/DavidJinkinsCV.pdf}

% The following metadata will show up in the PDF properties
\hypersetup{
    colorlinks = true,
    urlcolor = black,
    pdfauthor = {\name},
    pdfkeywords = {economics, statistics, mathematics},
    pdftitle = {\name: Curriculum Vitae},
    pdfsubject = {Curriculum Vitae},
    pdfpagemode = UseNone
}

\geometry{
    body={6.5in, 8.5in},
    left=1.0in,
    top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
    \begin{list}{}{
            \setlength{\leftmargin}{1.5em}
            \setlength{\parskip}{0pt}
            \setlength{\parsep}{0pt}
        }
    }{
    \end{list}
}

\begin{document}

% Place name at left
{\huge \name}
\hrule

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{4mm}

\begin{minipage}{0.45\linewidth}
    \hspace*{5mm}\href{http://www.psu.edu/}{Penn State University} \\
    \hspace*{5mm}Department of Economics \\
    \hspace*{5mm}Kern Building \\
    \hspace*{5mm}State College, PA 16802
\end{minipage}
\begin{minipage}{0.45\linewidth}
    \begin{tabular}{ll}
        Phone: & (814) 753-0181 \\
    %Fax: &  (919) 962-5678 \\
        Email: & \href{mailto:david.jinkins@gmail.com}{\tt david.jinkins@gmail.com} \\
        Homepage: & \href{http://www.davidjinkins.com}{\tt http://www.davidjinkins.com} \\
    \end{tabular}
\end{minipage}

\vspace{7mm}
{\Large Education}
\vspace{1mm}
\hrule

\begin{itemize}
    \item PHD Economics (expected), The Pennsylvania State University, 2014,\\
        \hspace*{1cm}\emph{Fields: Trade, Development, Game Theory.}

    \item MA Economics, National Taiwan University, 2009,\\
        \hspace*{1cm}\emph{Masters Thesis: "A Bridge Goes Both Ways: A Two-Way Migration Model with Incomplete Information \hspace*{1cm}and Social Capital".}

    \item BA Political Science, Carleton College, 2005.\\
        \hspace*{1cm}\emph{Magna Cum Laude}
\end{itemize}

\vspace{4mm}
{\Large Working Papers}
\vspace{1mm}
\hrule
\begin{itemize}
    \item Peer Learning, Labor Movement, and Knowledge Diffusion
    \item A Structural Comparison of Conspicuous Consumption in China and the United States.
    \item A Search and Learning Model of Export Dynamics (\emph{with Jonathan Eaton, Marcela Eslava, C.J. Krizan, and Jim Tybout}).
\end{itemize}

\vspace{4mm}
{\Large Work in Progress}
\vspace{1mm}
\hrule
\begin{itemize}
    \item Trade on an Evolving Network (\emph{with Jonathan Eaton, C.J. Krizan, Jim Tybout, and Daniel Xu}).
    \item Market Shocks and Newspaper Ideology: Evidence from Taiwan (\emph{with Chun-Fang Chiang and Long-Yu Chiou})
\end{itemize}

\vspace{4mm}
{\Large Employment}
\hrule
\begin{itemize}
    \item Penn State University, Research Assistant Summer 2011--present.
    \item Penn State University, Teaching Assistant Spring 2011.
    \item National Taiwan University, Research Assistant 2008--2009,
    \item K International Transport Company, Freight Forwarder 2005--2006,
\end{itemize}

\vspace{4mm}
{\Large Awards}
\vspace{1mm}
\hrule
\begin{itemize}
    \item Rosenberg Award, 2013
    \item National Science Foundation East Asia and Pacific Summer Institute Fellowship, China 2012.
    \item Penn State University, Graduate Research Assistant Fellowship 2009--Spring 2011.
    \item Ministry of Education Taiwan Scholarship, Taiwan 2007--2009.
    \item U.S. Fulbright Fellowship, Turkey 2006--2007.
    \item Chang-Lan Fellowship, China 2003.
\end{itemize}

\vspace{4mm}
{\Large Service}
\vspace{1mm}
\hrule
\begin{itemize}
    \item 2013 Penn State JMP Conference, Organizer (with Kala Krishna and Suraj Shekhar)
\end{itemize}

\vspace{4mm}
{\Large Presentations}
\vspace{1mm}
\hrule
\begin{itemize}
    \item 2012 NSF Summer Institute, Beijing
    \item 2014 University of British Colombia, Sauder School of Business
    \item \ \ \ \ \ \ \ \ Hitotsubashi University
    \item \ \ \ \ \ \ \ \ Singapore Management University 
    \item \ \ \ \ \ \ \ \ University of Cambridge
    \item \ \ \ \ \ \ \ \ Copenhagen Business School 
\end{itemize}

\vspace{4mm}
{\Large References}
\vspace{1mm}
\hrule
\begin{itemize}
    \item Jonathan Eaton, \emph{Brown University}, Jonathan\_Eaton@brown.edu
    \item Kala Krishna, \emph{Penn State University}, kmk4@psu.edu
    \item Jim Tybout, \emph{Penn State University}, jxt32@psu.edu (\textbf{advisor})
\end{itemize}

\vspace{7mm}
{\Large Personal}
\vspace{1mm}
\hrule

\begin{itemize}
    \item Citizenship: United States.
    \item Languages: English, Mandarin Chinese, Turkish.
    \item Technical: python, matlab, vim, \LaTeX, Stata, html, css, bash, C++.
\end{itemize}

% Footer
\begin{center}
    \begin{footnotesize}
        Last updated: \today .\\
        \href{\footerlink}{\texttt{\footerlink}}
    \end{footnotesize}
\end{center}

\end{document}
